---
title: "Machine Learning - Peer Assesment"
author: "Carlos Figueroa"
date: "31 de octubre de 2016"
output: html_document
---
  
##Intro
  
The main idea is to predict the activitie that is being performed bya  group of people by using the data provided by activity monitors

## Main Procedure

Lets start by setting the working directory, loading the data, preeeliminar analysis, etc.

```{r results='hide', message=FALSE, warning=FALSE}
library(knitr)
library(caret)
library(e1071)
library(rpart)
library(rattle)
library(rpart.plot)
```

```{r}
setwd("C:\\Users\\figuca02\\datasciencecoursera\\Machine_Learning_Submission")
training<-read.csv("pml-training.csv")
testing<-read.csv("pml-testing.csv")
```

Creating partition and the subsequent training and testing sets:
  
```{r}
inTrain <-createDataPartition(training$classe, p=0.7, list=FALSE)
trainset<-training[inTrain, ]
testset<-training[-inTrain, ]
```

Seems there are a lot of variables, some useless like identifiers, so in order to take the most relevant ones I will remove non zero variance and change NA to 0 and remove the first variables which are only identifiers of time and subjet:
  
```{r}
trainset[is.na(trainset)]<-0
testset[is.na(testset)]<-0
nonzerovar<-nearZeroVar(trainset)
trainingset<-trainset[,-nonzerovar]
testingset<-testset[,-nonzerovar]
trainingset<-trainingset[,-(1:5)]
testingset<-testingset[,-(1:5)]
names(trainingset)
names(testingset)
```


## Prediction

Now, with the remaining 54 variables I will try a simple classification tree prediction:
  
```{r}
set.seed(1234)
modelfit<-rpart(classe~., data=trainingset, method="class")
fancyRpartPlot(modelfit)
```


Predicting on the training dataset:
  
```{r}
set.seed(1234)
predictmodelfit<-predict(modelfit, data=trainingset, type="class")
confusionMatrix(predictmodelfit,trainingset$classe)
```


Predicting on the test set:
  
```{r}
set.seed(1234)
predicttest<-predict(modelfit, newdata=testingset, type="class")
confusionMatrix(predicttest, testingset$classe)
```


Now, for the test:
  
```{r}
set.seed(1234)
predictnewtest<-predict(modelfit, newdata=testing)
predictnewtest
```
